\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{fullpage}

\newtheorem{thm}{Theorem}
\theoremstyle{definition}
\newtheorem{exmpl}{Example}
\newtheorem{defn}{Definition}

\begin{document}

\title{CS 360 Notes}
\author{Matthew Visser}
\date{Nov 24, 2011}
\maketitle

\section{Universal Turing Machine}

\begin{equation}
	L = \{(f(M),w):w \in L(M) \}
\end{equation}

This language is recursively enumerable:
\[U(T,w)\]
\begin{itemize}
	\item If $M$ accepts $w$, then $U$ will accept $f(M),w)$.
	\item If $M$ rejects $w$, then $U$ will reject $f(M),w)$.
	\item If $M$ loops forever on $w$, then so will $U$ on $(F(M),w)$.
\end{itemize}

How do we make $U$?

Simultate $M$ on input $w$, we want to keep track of
\begin{itemize}
	\item current state of $M$'s tape.
	\item Current state in $M$.
	\item Scratch work.
\end{itemize}

\begin{thm}
	By way of contradiction, assume that there exists a TM $U'$ that decides
	$L_U$. We'll show that the existence of $U'$ implies that $L_{NSA}$ is
	decideable.

	\begin{proof}
		Here is hwo to make $M_{NSA}$ that decides $L_{NSA}$ on input $w$:
		\begin{itemize}
			\item Run $U'$ on input $w,w$
			\item If $U'$ accepts $(w,w)$, then reject.
			\item If $U'$ rejects $(w,w)$, then accept.
		\end{itemize}
	\end{proof}
\end{thm}

\begin{thm}
	$L_{SA}$ is not decideable.
	\begin{proof}
		Argue that there doesn't exist any TM $M$ that decides $L_{SA}$.

		Suppose we have a machine $M'$ that decides $L_{SA}$. Recall
		$L_{NSA}$ isn't decideable. Therefore, $L_{SA}$ is not decideable.
	\end{proof}
\end{thm}

\begin{thm}
	If $L$ is decideable, then so is its complement, $L'$.
	\begin{proof}
		Since $L$ is decideable, $\exists M$ that decides $L$. Construct $M'$
		that decides $L'$ by running $L$ and then reversing the result.
	\end{proof}
\end{thm}

Given that $L$ and its complement, $L'$, are recursively enumerable, is $L$
necessarily decideable?

Let $M$ be a machine where $L(M) = L$.
Let $M'$ be a machine where $L(M') = L'$.
Run both machines in tandem. On every input, one of the machines will accept
since the languages are complements. If $M$ accepts, then accept, if $M'$
accepts, then reject. We have built a machine that decides $M$.

The intersection of recursively enumerable languages are recursively enumerable:
\begin{itemize}
	\item Just run both TMs. If one accepts, run the other. Accept if it
		accepts.
\end{itemize}
The union of r.e. languages:
\begin{itemize}
	\item Run both and accept if either one accepts.
\end{itemize}

Given $f(M)$, is the language of $M$ non-empty?
\begin{equation}
	L_{NE} = \{w | w = f(M) \land L(M) \neq \emptyset\}
\end{equation}
Is $L_{NE}$ recursively enumerable? Try every word.

\end{document}
% vim: tw=80
