\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{fullpage}

\begin{document}

\newtheorem{thm}{Theorem}

\title{CS 360 Notes}
\author{Matthew Visser}
\date{Nov 29, 2011}
\maketitle

\begin{equation}
	L_{NE} = \{ f(M): L(M) \neq \emptyset \}
\end{equation}
Show that $L_{NE}$ is not decidable.

\textbf{Problem}:

Given a TM $M$, is its language empty?

We'll show that this problem is not decidable.

$U'$ is the universal decider: It takes $(M,w)$, accepts if $w \in L(M)$. We
showed earlier that $U'$ does not exist.

Assume by way of contradiction that there is a machine $M_{NE}$ that decides
$L_{NE}$. This will imply that $U'$ exists. Because it does not exist, this is a
contradiction. So $L_{NE}$ is not decidable.

If $U'$ accepts then $M_{NE}$ accepts $M$. So $L(M') \neq \emptyset$. So $L(M')
= \{0,1\}^*$. So $M$ accepts $w$. If $U'$ rejects, then $M_{NE}$ rejected $M'$,
so $L(M') = \emptyset$. So $M$ doesn't accept $w$.

\begin{equation}
	L_E = \{ f(M): L(M) = \emptyset \}
\end{equation}

Is this decidable? Recursively enumerable?

What's the complement of $L_E$? $L_{E}' = L_{NE} \cup \{w | w \text{ is not the
encoding of any Turing machine}\}$.

Is $L'_{E}$ r.e.? Yes.

So if $L_{E}$ is r.e., then $L_{E}$ and $L'_E$ are recursively enumerable. If
$L'_E$ is decidable, then so is  $L_{NE}$ Therefore $L_E$ is not recursively
enumerable.

\begin{thm}
	$L_e$ is not r.e. and so also not decidable.
	\begin{proof}
		We know that $L_{NE}$ is .r.e.
		\begin{enumerate}
			\item $L'_e = L_{NE} \cup \{ w | \text{$w$ is not an encoding of a
				Turing Machine}\}$
			\item Since $L_{NE}$ is r.e., so is $L'_e$.
			\item Assume that $L_E$ is r.e.
			\item So $L_e$ and $L'_E$ are both decidable.
			\item Since $L'_E$ is decidable, so is $L_{NE}$, A contradiction.
		\end{enumerate}
	\end{proof}
\end{thm}

\begin{equation}
L_\infty = \{f(M): L(M) = \infty \}
\end{equation}

$L_\infty$ is undecidable.



\end{document}
% vim: tw=80
