\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{fullpage}

\newtheorem{thm}{Theorem}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{exmpl}{Example}
\begin{document}

\title{CS 360 Notes}
\author{Matthew Visser}
\date{Nov 15, 2011}
\maketitle

\section{Pumping Lemma For CFG}

\begin{thm}
Let $L$ be a language. Suppose that $\forall n > 0$: there exists a word
$z \in L$ with $|z|>n$ such that any division of $z = uvwxy$ where $|vwx|\le n$
there exists an $i \ge 0$ such that $uv^iwx^iy \notin L$ then $L$ is not
context-free.
\end{thm}

\begin{exmpl}

$L = \{a^ib^ic^i|i \ge0\}$

Consider $z = a^nb^nc^n$ with a decomposition $z=uvwxy$ where $|vwx|\le n$ and
$|vx| \ge 0$.

$v$ and $x$ consist of at most 2 types of characters, that is $vx$ can include
all of $a$,$b$, and $c$, because otherwise $vux$ would have to be at least $n+1$
characters. Say $i=2$. $uv^2wx^2y \notin L$ because at most 2 types of
characters occur more often than in $z$, but not all the types.
\end{exmpl}

\begin{exmpl}
	$L = \{ a^ib^jc^k|i<j, i<k\}$

	$z = a^nb^n+1c^n+1$

	Consider any decomposition of $z$ into $uvwxy$.

	\begin{enumerate}
		\item[Case 1.] Contains no $a$'s. $i=0$ drops the numbers of b or c, and
			they coudl be 0, so then it wouldn't be in the language.
		\item[Case 2.]  \dots bored
	\end{enumerate}
\end{exmpl}

\section{Closure Properties for CFGs}

Regular languages are closed under: union, complement, intersection, reversal,
concatenation, kleene star.

\subsection{Union}

$G_1: S_1\to\dots$

$G_2: S_2 \to \dots$

$G: S \to S_1 | S_2$

\subsection{Concatenation}

$G: S \to S_1S_2$

\subsection{Kleene Star}

$G: S \to SS_1 | \varepsilon$

\subsection{Reversal}

Create $G$ by reversing all production rules.

\subsection{Intersection}

$L = \{a^ib^ic^i|i \ge 0\}$, which is not context-free.

$L_1 = \{a^ib^ic^j| i,j \ge 0\}$

$L_1 = \{a^jb^ic^i| i,j \ge 0\}$

$L_1 \cap L_2 = L$ which is not context-free.

\section{Number of Steps}

\begin{thm}
	Consider a word $w$ where $|w| = n$, then any derivation of $w$ in a grammar
	in CNF will have $2n-1$ steps.
\end{thm}

Given a CFG, does the language include the word $w$?

Convert this grammar to CNF. Enumerate all derivations of length
$2|w| - 1$ and see if any of them derive $w$.

\section{Turing Machines}


\end{document}
% vim: tw=80
