\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{fullpage}

\begin{document}

\title{CS 360 Notes}
\author{Matthew Visser}
\date{Sep 29, 2011}
\maketitle

\textbf{Submit assignment}: on third floor in the pink assignment boxes.

\textbf{For 3.b.}
For counting minimal \dots

Define variable $t$ as the number of characters output by the algorithm.

Can assume given a state $s$ and character $a$, $\delta(s,a) = O(1)$.

\textbf{For 3.c.}

\section{Kleene's Theorem}

We proved one direction last class, now we will do the other direction.

We can remove states and repolace them with a regular expression.

\subsection{Removing states}

\begin{itemize}
    \item Add a new start state with $\varepsilon$-transition to the old start
        state
    \item Add a new accepting state, $f_1$ with an $\varepsilon$-transition from
        all old accepting states.
    \item For each state $1$ what isn't the new start oj accepting state.
        \begin{itemize}
            \item For all state pairs $p,r$ that go through $q$
                \begin{itemize}
                    \item Let $e_1$ be the label of edge from $p$ to $q$
                    \item Let $e_2$ be the label of edge from $q$ to $r$
                    \item Let $e_3$ be the label of loop from $q$ to itself.
                    \item Let $e_4$ be the label of the edge from $p$ to $r$.
                    \item Replace label from $p$ to $r$ with $(e_4 +
                        e_1e_3^*e_2)$.
                \end{itemize}
            \item Remove state $q$.
        \end{itemize}
    \item End process when only state is accepting state.
\end{itemize}

\section{The Pumping Lemma}

We want a way to prove that a language is not regular.

A language $L$ is not regular if for every finite automata $M$, $L \neq L(M)$.

Let's say $M$ has $n$ states, $k>n$. This means that if we have a word longer
than the number of states, then there must be a loop.

Given a F.A. $M$ with $n$ states and a word $x \in L(M)$ where $|x| \geq n$, $x$
can be divided as $x = uvw$ where
\begin{itemize}
    \item $|uv| \leq n$
    \item $|v| \geq 1$
    \item $uv^*w \subseteq L(M)$
\end{itemize}

\subsection{The Formal Pumping Lemma}

Given a regular language $L$, $\exists n>0$ such that all words, $x\in L,\
|x|\geq n$ can be divided into $u,v,w$ where
\begin{itemize}
    \item $uv\leq n$
    \item $v \neq \varepsilon$
    \item $uv^iw \in L\quad \forall i\geq 0$
\end{itemize}

Let $L$ be a language. Suppose that for any positive integer $n$ there exists a
word $x\in L,\ |x|\geq n$ such that for any division of $x$ into $x=uvw$ with
$|uv|\leq n$ and $v \neq \varepsilon$. It is not the case that $uv^*w \subseteq
L$. Then $L$ is not a regular language.

\subsection{Example}

\[
L = \{0^i1^i|i\geq0\} = \{\varepsilon,01,0011,000111,\dots\}
\]
is not a regular language.

We must show no matter what $n$ we have, we cannot ``pump out'' some substring
$v$.

Consider all decompositions $x = uvw$ where $|uv|\geq n$ and $v \neq
\varepsilon$.

Choose $x = 0^n1^n$.

$\because \exists i | uv^iw \not \in L$, this is not a regular language.
\qed

\end{document}
% vim: tw=80
