\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}
\usepackage{enumerate}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{fullpage}

\begin{document}

\title{CS 360 Notes}
\author{Matthew Visser}
\date{Oct  4, 2011}
\maketitle

\textbf{A2 Posted}

\section{Pumping Lemma}

\textbf{Definition}:

Given a regular language $L$, there ixists some positive $n$ such that $\forall
x \in L$ with $|x|\geq n$, $x$ can be divided into $x = uvw$, where:
\begin{itemize}
	\item $|v|>0$
	\item $|uv|\leq n$
	\item $uv^iw\in L \forall i \geq 0$
\end{itemize}

\textbf{Example}:

$L = \{ 0^p | p \text{ is prime } \} = \{00,000,00000,0000000,\dots\}$

To show that $L$ is not regular, find a word, $x$, so that for any $n$, 
$|w|\geq n$. FOr any decomposition of $x$ into $uvw$ where \begin{enumerate}
	\item $|v|>0$
	\item $|uv|\geq n$
\end{enumerate}
$\exists$ some $i$ so that $uv^iw \notin L$

If $L$ was regular, then $\forall j \geq 0, uv^jw \in L$. To show that it is not
regular, we need to find one value of $j$ such that $uv^jw \notin L$.

How many 0's are there in $uv^iw$? There are $q$ for $u$, $p-q$ for $w$, and $i$
for $v$. So we find $j$ so that $ji + p-i$ is not prime. Set $j = p-i$, then
$|uv^jw = j\cdot i + p - i = (i+1)(p-i)$ which is composite. Therefore the
language is not regular.

\textbf{Example}

$\Sigma = \{0,1\}$,
$L = \{ s\ |\ s \in \Sigma,\ s = s^R \}$ \textit{i.e.} the language of
palindromes.

Consider \underline{any} composition of $x$ into $uvw$ so that it meets the
conditions of the pumping lemma.

$v = 0^j\ j \geq 1$.

Show that $\exists i$ so that $uv^iw \notin L$.

Set $i=0$. Is $uw \in L$? Have $uw=0^{n-j}10^n$, so no.

\textbf{Another Example}

$L = \{y!z \ |\ |y| >|z|,\ y,z \in \{0,1\}^* \}$

Let $x = 0^{n+1}!1^n$

Consider any decomposition of $x$ into $uvw$ so that $|uv| \leq n $ and $v \neq
\varepsilon$. What does $v$ look like? $v = 0^j$ fo some $j\geq i$. Let's try
$i=0$. $uv^iw = uw = 0^{n+1-n}!1^n$. This is not in the language because the
number of 0's must be greater than the number of 1's.

\subsection{What Can Go Wrong}

It's easy to misuse the pumping lemma.

\textbf{One bad decomposition doesn't matter:}

Must show that all decompositions $x = uvw$ with $|uv \leq n$ and $v \neq
\varepsilon$ can't be pumped.

Consider $L = (01)^*$. This is reqgular. If we use the pumping lemma
incorrectly, we could show this is irregular. Choose a word $(01)^n$.

Take $u=0,\ v=1,\ w=(01)^{n-1}$

$uv^2w = 011(01)^{n-1}$.

You can't choose:
\begin{itemize}
	\item $n$, but we choose the word in terms of $n$.
	\item The decomposition, but we choose the number of times to pump $v$.
\end{itemize}

\textbf{The Contrapositive}: If all the words in the language can be pumped, it
doesn't necessarily mean that the language is regular. This means you can't use
this lemma to show that a language is regular.

\section{Subsets}

Given $L$ is regular, $L_1 \subseteq L$. Is $L_1$ necessarigly regular


\end{document}
% vim: tw=80
